Loss recovery and tail loss performance in Multipath TCP

### 2017-01-15 main.tex
Update

Through this set of preliminary experiments, we would like to understand the behavior of MPTCP with and without TLP and ER by monitoring burst completion time, congestion window evolution and timeout 
behavior.

@@

We try to understand the loss recovery and retransmission policies in state of the art MPTCP linux implementation version 0.91. As per the specification of Multipath TCP introduced in 
MPTCP features acknowledgements at connection-level as well as subflow-level, in order to provide a robust transport service to the application.

@@

Retransmission behavior of TCP is seen a base case for MPTCP performance as each individual MPTCP subflow is a TCP flow in itself. Our analysis
starts with the results using TCP and compares it with that of the MPTCP. Figures ~\ref{t1p},~\ref{t2p},~\ref{t1pp} represent the comparison of TCP 
burst completion times. Path asymmetry is irrelevant as the TCP uses single path.

@@

The expected retransmission behavior of MPTCP for different settings of ER is shown 
in~\ref{timingER0},~\ref{timingER2} and ~\ref{timingER3}.

\begin{figure}[!ht]
\begin{center}
\includegraphics[angle=0, width=0.45\textwidth, natwidth=610, natheight=400]{images/timingER0.pdf}
\end{center}
\caption{Timing diagram of different tail loss scenarios in sysctl ER=0}\label{timingER0}
\end{figure}

\begin{figure}[!ht]
\begin{center}
\includegraphics[angle=0, width=0.45\textwidth, natwidth=610, natheight=400]{images/timingER2.pdf}
\end{center}
\caption{Timing diagram of different tail loss scenarios in sysctl ER=2}\label{timingER2}
\end{figure}

\begin{figure}[!ht]
\begin{center}
\includegraphics[angle=0, width=0.45\textwidth, natwidth=610, natheight=400]{images/timingER3.pdf}
\end{center}
\caption{Timing diagram of different tail loss scenarios in sysctl ER=3}\label{timingER3}
\end{figure}

@@

To further study the performance of TLP in improving latency, we tried to drop the probe packet along with the last packet. In this case ER=0
setting results much lower burst completion times. Use of TLP did not improve the burst completion time as we saw in TCP for ER=3. The reason
lies in the way the retransmission and loss probe transmission carried out in MPTCP. Retransmission occurs after an RTO time on both paths.
Even if retransmission fails on one path, the client receives the packet on the other path as shown in Fig~\ref{timingER0}. For TLP, in
current implementation, the loss probe sent on the actual path of first transmission but not on both paths. This incorrect impartation of
TLP from TCP to MPTCP led to the increase burst completion time by an RTO for MPTCP.

@@

\section{Proposed changes and expected implications}

\subsection{Implementation Plan}

Things to do:

When PTO fires: in code trigger call on PTO in tcp level
It calls ${tcp\_push\_one()}$ in tcp-output.c and then ${mptcp\_write\_xmit()}$.
As it is reinjection (due to only one case currently in MPTCP), that packet will have path mask
to put it on the same subflow. Here we need to add a case for reinjection due to PTO that should
send the packet to $reinject\_queue$ of ${mptcp\_cb}$ as well.

Main flow packet queue and subflow packet queue: ${meta\_sk}$ refers to the
main mptcp flow.

Loss probe timer used in Linux: ${ICSK\_TIME\_LOSS\_PROBE}$.

>>>>

@@

This paper presents the state of the art loss recovery mechanism of MPTCP and presents case for improvement in the tail loss scenario. For understanding the loss recovery and retransmission policies 
in state of the art MPTCP linux implementation version 0.91, we consider specific cases of tail losses.

@@

\subsection{TCP}
Retransmission behavior of TCP is seen a base case for MPTCP performance as each individual MPTCP subflow is a TCP flow in itself. Our analysis
starts with the results using TCP and compares it with that of the MPTCP. Figures ~\ref{t1p},~\ref{t2p},~\ref{t1pp} represent the comparison of TCP 
burst completion times. Path asymmetry is irrelevant as the TCP uses single path.

@@

\subsection{MPTCP}

The expected retransmission behavior of MPTCP for different settings of ER is shown 
in~\ref{timing1P},~\ref{timing1PP} and ~\ref{timing2P}.

\begin{figure}[!ht]
\begin{center}
\includegraphics[angle=0, width=0.45\textwidth, natwidth=610, natheight=400]{images/timing1P.pdf}
\end{center}
\caption{Timing diagram of MPTCP behavior with one packet tail loss a) STD b) LIN}\label{timing1P}
\end{figure}

\begin{figure}[!ht]
\begin{center}
\includegraphics[angle=0, width=0.45\textwidth, natwidth=610, natheight=400]{images/timing1PP.pdf}
\end{center}
\caption{Timing diagram of MPTCP behavior with one packet and next probe loss a) STD b) LIN}\label{timing1PP}
\end{figure}

\begin{figure}[!ht]
\begin{center}
\includegraphics[angle=0, width=0.45\textwidth, natwidth=610, natheight=400]{images/timing2P.pdf}
\end{center}
\caption{Timing diagram of MPTCP behavior with two packet tail loss a) STD b) LIN}\label{timing2P}
\end{figure}

@@

To further study the performance of TLP in improving latency, we tried to drop the probe packet along with the last packet. In this case ER=0
setting results much lower burst completion times. Use of TLP did not improve the burst completion time as we saw in TCP for ER=3. The reason
lies in the way the retransmission and loss probe transmission carried out in MPTCP. Retransmission occurs after an RTO time on both paths.
Even if retransmission fails on one path, the client receives the packet on the other path as shown in Fig~\ref{timing1P}. For TLP, in
current implementation, the loss probe sent on the actual path of first transmission but not on both paths. This incorrect impartation of
TLP from TCP to MPTCP led to the increase burst completion time by an RTO for MPTCP.

@@
